---
title: "Meta-Analysis Simulation"
author: "Niki Petrakos"
date: "July 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stacomirtools)
library(simsalapar)
```


```{r, replications}
## Create setup for simulation
varList <- varlist(
  n.sim = list(type = "N", expr = quote(N[sim]), value = 100000),  # make value larger once this starts working
  K = list(type = "grid", value = c(5, 15, 25)),
  M = list(type = "grid", value = c(20, 800)),
  MSDratio = list(type = "grid", value = c(1/3, 1/2)),
  tau = list(type = "grid", value = c(0.2313, 0.4314, 0.6725)),
  lambda = list(type = "frozen", value = 2)
)

## Define function for 1 simulation
doOne <- function(K, M, MSDratio, tau, lambda){

  ## Generate number of studies and determine at which studies to perform an inspection
  numstudies <- rpois(K, 1.5)
  numstudies <- ifelse(numstudies[] == 0, 1, numstudies[])  # set any 0's to 1
  inspect <- cumsum(numstudies)  # this tells us at which studies we perform an inspection
  numstudies_total <- sum(numstudies)  # total number of studies generated


  ## We have Treatment Group X and Treatment Group Y; simulate standard deviations and sample sizes
  studylabel <- c(1:numstudies_total)  # assign labels to each study
  N <- ceiling(rnorm(numstudies_total, M, MSDratio*M))
  N <- ifelse(N[] < 20, 20, N[])  # if N < 20, set the total sample size to 20
  samplesize_ratio <- runif(numstudies_total, min = 0.4, max = 0.6)  # ratio = n_1j / N
  n_1j <- samplesize_ratio*N
  n_2j <- N-n_1j

  # dataframe of all study data
  studydata <- data.frame("Study" = studylabel, "Sample Size X" = n_1j, "Sample Size Y" = n_2j, check.names=FALSE)


  ## Next: simulate tau's, within-study variation, and treatment difference (delta j)
  if(tau == 0.2313){
    mix1 <- runif(ceiling(0.5*numstudies_total), min=0.1, max = 1)
    mix2 <- runif(ceiling(0.5*numstudies_total), min=1, max = 1/0.1)
    mixcombo <- c(mix1, mix2)
    ratio_sigmatau <- sample(mixcombo)
  }

  if(tau == 0.4314){
    mix1 <- runif(ceiling(0.5*numstudies_total), min=0.2, max = 1)
    mix2 <- runif(ceiling(0.5*numstudies_total), min=1, max = 1/0.2)
    mixcombo <- c(mix1, mix2)
    ratio_sigmatau <- sample(mixcombo)
  }

  if(tau == 0.6725){
    mix1 <- runif(ceiling(0.5*numstudies_total), min=0.3, max = 1)
    mix2 <- runif(ceiling(0.5*numstudies_total), min=1, max = 1/0.3)
    mixcombo <- c(mix1, mix2)
    ratio_sigmatau <- sample(mixcombo)
  }

  if(is.odd(numstudies_total)){
    ratio_sigmatau <- head(ratio_sigmatau, -1)
  }

  # within-study variation (standard deviation)
  sigma_study <- ratio_sigmatau*tau  
  studydata[, "Study SD"] <- sigma_study  # add within-study variation to dataframe

  # treatment difference (sample mean difference)
  delta_j <- rnorm(numstudies_total, 0.2, tau)  # per study
  D_j <- rnorm(numstudies_total, delta_j, sqrt((sigma_study^2/n_1j)+(sigma_study^2/n_2j)))  # sample mean difference follows normal distribution
  studydata[, "Sample Mean Diff"] <- D_j  # add sample mean difference to dataframe


  ## Next: find (cumulative) test statistics at each study, adjusted and naive
  I_jplus <- ((sigma_study^2/n_1j)+(sigma_study^2/n_2j)+tau^2)^(-1)  # information/precision including tau in calculation, per study
  
  I_j <- ((sigma_study^2/n_1j)+(sigma_study^2/n_2j))^(-1)  # information/precision not including tau in calculation, per study
  
  S_k <- cumsum(I_jplus*D_j)  # weighted estimator of treatment difference
  
  I_ckplus <- cumsum(I_jplus)  # cumulative information including tau
  
  I_ck <- cumsum(I_j)  # cumulative information without tau
  
  lnpenalty <- log(log(I_ck))
  
  lnpenalty <- ifelse(lnpenalty[] < 1, 1, lnpenalty[])  # ln(ln(I_ck)) is set to 1 if it is smaller than 1 (to be conservative)
  
  teststat <- S_k/sqrt(lambda*I_ckplus*lnpenalty)
  
  studydata[, "Cum Test Stat"] <- teststat  # add cumulative test statistics to dataframe

  teststat_naive <- S_k/sqrt(I_ckplus)
  
  studydata[, "Cum Naive Test Stat"] <- teststat_naive  # add naive cumulative test statistics to dataframe
  
  
  ## Next: determine if committed false positive

  # only check at studies that coincide with an inspection
  
  numfp <- numeric(length(inspect))  # keep track of number of false positives 
  
  naive_numfp <- numeric(length(inspect))  # naive false positives
  
  for(i in 1:length(inspect)){
    numfp[i] <- ifelse(abs(teststat[inspect[i]]) > 1.96, 1, 0)
    naive_numfp[i] <- ifelse(abs(teststat_naive[inspect[i]]) > 1.96, 1, 0)
  }
  index  <- c(ifelse(sum(numfp)==0,0,
                 inspect[which.max(numfp)]), 
            ifelse(sum(naive_numfp)==0,0,
                 inspect[which.max(naive_numfp)]))

  return(index)
}

res <- doLapply(varList, doOne = doOne)

youres = getArray(res)

youres_df = array2df(youres)

meanindex <- youres_df %>% group_by(tau,K) %>% summarise(mean=mean(value[1])) %>% 
  spread(key=tau, value=mean)

meanindex_naive <- youres_df %>% group_by(tau,K) %>% summarise(mean=mean(value[2])) %>% 
  spread(key=tau, value=mean)

#ggplot(youres_df %>% filter(D.1==1), aes(x=value)) + geom_bar()  # adjusted

#ggplot(youres_df %>% filter(D.1==2), aes(x=value)) + geom_bar()  # naive

#ggplot(subset(youres_df, tau == 0.2313, D.1 == 1), aes(x=value)) + geom_bar()

theme_update(plot.title = element_text(hjust = 0.5), text = element_text(size=12))

ggplot(youres_df %>% filter(D.1==1), aes(x=value)) + geom_bar(width=5) + facet_grid(.~tau) + ggtitle("Rejection Count: Adjusted Test Stat, Levels of Tau, delta j = 0")

ggplot(youres_df %>% filter(D.1==2), aes(x=value)) + geom_bar(width=5) + facet_grid(.~tau) + ggtitle("Rejection Count: Naive Test Stat, Levels of Tau, delta j = 0")

ggplot(youres_df %>% filter(D.1==1), aes(x=value)) + geom_bar(width=5) + facet_grid(.~K) + ggtitle("Rejection Count: Adjusted Test Stat, Levels of K, delta j = 0")

ggplot(youres_df %>% filter(D.1==2), aes(x=value)) + geom_bar(width=5) + facet_grid(.~K) + ggtitle("Rejection Count: Naive Test Stat, Levels of K, delta j = 0")


```

return the index which contains two values (index of proposed test statistic when it first goes above if ever, when the naive went above)
compute proportion of times the first number is 0 over the number of replications, do the same for the second value (naive one should be too large)
when it goes above: make bar graph/histrogram for when it happens (naive should stop quite early)
do the bar graph for all 100,000 replications

then, try 0, 0.2, 0.4



